Approximation as Differentiation

### 2025-06-07 main/higher-order.tex
Note on grad-CAM.
Add language section.

\section{Interpreting Higher-Order Programs}
\label{sec:higher-order}

$\Fam(\FinVect)$ and $\Fam(\LatGal)$ provide appropriate notions of composition for automatic differentiation
and Galois slicing respectively, but neither is Cartesian closed and thereby able to interpret higher-order
programs directly. However the following is a special case of a construction due to \citet{nunes2023}:

@@

Abusing notation somewhat, we shall write $X$ for an object $(X, \partial X)$ in $\Fam(C)$, and similarly for
morphisms $f = (f, \partial f)$. If $\cat{C}$ has all small products and also biproducts, then the internal
hom $\internalHom{X}{Y}$ in $\Fam(\cat{C})$ is the object $Z$ where:
\begin{itemize}
\item the indexing set $Z$ is the $\Fam(\cat{C})(X, Y)$, which is indeed a set by
\propref{Grothendieck:fam-inherits-local-smallness};
\item the indexed family $\partial Z$ is the family of products $\prod_{X}\reindex{\partial Y}{f}$ for every
${f: X \to Y}$.
\end{itemize}

>>>>

\section{CHAD at Higher-Order}
\label{sec:higher-order}

$\Fam(\FinVect)$ and $\Fam(\LatGal)$, introduced in \secref{first-order}, provide appropriate notions of
composition for automatic differentiation and Galois slicing respectively, but neither is Cartesian closed and
thereby able to interpret higher-order programs directly. However the following is a special case of a
construction due to \citet{nunes2023}:

@@

Abusing notation somewhat, we shall write $X$ for an object $(X, \partial X)$ in $\Fam(C)$, and similarly for
morphisms $f = (f, \partial f)$. If $\cat{C}$ has all small products and also biproducts, then the internal
hom $\internalHom{X}{Y}$ in $\Fam(\cat{C})$ is the object $Z$ where:
\begin{itemize}
\item the indexing set $Z$ is $\Fam(\cat{C})(X, Y)$, which is indeed a set by
\propref{Grothendieck:fam-inherits-local-smallness};
\item the indexed family $\partial Z$ is the family of products $\prod_{X}\reindex{\partial Y}{f}$ for every
${f: X \to Y}$.
\end{itemize}
